### 2016-02-07 ch05-initvals/InitialValuesPaper.tex
Some changes to initval

In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval $\mathrm{CI}$) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
Note that the empirical count of successes $n_{\mathrm{success}}$ out of the $N_{\MC}$ total observations is binomially distributed with success rate $\eta$.
The computation of confidence bounds of such a variable is not obvious due to the discrete nature of the variable: $n_{\mathrm{success}}$ can only attain a discrete set of values: $\Set{0,1,\ldots, N_{\MC}}$ whereas the true success rate $\eta$ is real-valued (but limited to the interval $[0,1]$).
The inherent discreteness of $\hat{\eta} \isdef n_{\mathrm{success}}/N_{\MC}$ and the difficulties this presents has sparked a fair amount of research to compute confidence bounds~\citep{Barnard1947Significance,Mato1997,Ross2003,Clopper1934}.
A simple way to deal with this problem, is to make use of the central limit theorem which states that $n_{\mathrm{success}}/N_{\MC}$ is approximately normally distributed when $N_{\MC} \to \infty$.
In doing so, one e.g. obtains the Wald confidence bounds~\citep{Ross2003}:
\begin{equation}
\mathrm{CI}_{\mathrm{Wald}} \isdef \hat{\eta} \pm z_{1-\alpha/2} \sqrt{\hat{\eta} (1-\hat{\eta}/N_{\MC})}
\end{equation}
with $\alpha = 1 - 0.95$ for $95\%$ confidence bounds and $z_{1-\alpha/2}$ is the $1-\alpha/2$ quantile of a standard normal distribution, i.e. $z_{\beta} \isdef \mathrm{CDF}_{\NormalDistribution}^{-1}(\beta)$
which requires inversion of the \gls{CDF} of a normal distribution.
However, such an approximation is overly optimistic when $n_{\mathrm{success}}$ approaches the boundaries of its domain (i.e. when $\eta \approx 0$ or $\eta \approx 1$) since normal confidence regions are always symmetrical whereas the actual success rate is inherently bounded as $0 \leq \eta 1$~\citep{Ross2003}.
An alternative method that does not approximate the binomial distribution by a normal one, is the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \code{binofit}).
In particular, this method relies upon the exact binomial distribution, which is why the method is often quoted as the `exact' method.
In particular, the $(1-\alpha)$  confidence bounds on $\eta$ are given by~\citep{Clopper1934}
\begin{equation}
 \mathrm{CI}_{\mathrm{ClopperPearson}} \isdef
 \left[
  \mathrm{CDF}_B^{-1}(\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)
  \;,\;
  \mathrm{CDF}_B^{-1}(1-\alpha/2; n_{\mathrm{success}} + 1, N_{\MC} - n_{\mathrm{success}})
 \right]
\end{equation}
where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution that is closely related to the Binomial distribution.
This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\onecolumnwidth]{\thisDir/fig/measurement.pdf}
  \caption[Measurement schematic of \BK\ 1613 filter.]{Schematic representation of the measurement set-up for the \BK\ 1613 filter. The AWG (Arbitrary Waveform Generator) and DAQ (Data Acquisition) hardware share the same clock and are thus synchronized. 
  Blue arrows indicate coax cables. 
  At the output of the bandpass filter, a noise generator is added that buffers the incoming signal using a TL071 opamp and adds white noise before passing the signal to the DAQ.} 
  \label{fig:measurementSetup}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  %\input{\thisDir/fig/bode-bk1613.tikz} %TODO: re-enable figure and make less dense
  \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.} 
  \label{fig:bk1613}
\end{figure}

>>>>

In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval $\mathrm{CI}$) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
Note that the empirical count of successes $n_{\mathrm{success}}$ out of the $N_{\MC}$ total observations is binomially distributed with success rate $\eta$.
The computation of confidence bounds of such a variable is not obvious due to the discrete nature of the variable: $n_{\mathrm{success}}$ can only attain a discrete set of values: $\Set{0,1,\ldots, N_{\MC}}$ whereas the true success rate $\eta$ is real-valued (but limited to the interval $[0,1]$).
The inherent discreteness of $\hat{\eta} \isdef n_{\mathrm{success}}/N_{\MC}$ and the difficulties this presents has sparked a fair amount of research to compute confidence bounds~\citep{Barnard1947Significance,Mato1997,Ross2003,Clopper1934}.
A simple way to deal with this problem, is to make use of the central limit theorem which states that $n_{\mathrm{success}}/N_{\MC}$ is approximately normally distributed when $N_{\MC} \to \infty$.
In doing so, one e.g. obtains the Wald confidence bounds~\citep{Ross2003}:
\begin{equation}
\mathrm{CI}_{\mathrm{Wald}} \isdef \hat{\eta} \pm z_{1-\alpha/2} \sqrt{\hat{\eta} (1-\hat{\eta}/N_{\MC})}
\end{equation}
with $\alpha = 1 - 0.95$ for $95\%$ confidence bounds and $z_{1-\alpha/2}$ is the $1-\alpha/2$ quantile of a standard normal distribution, i.e. $z_{\beta} \isdef \mathrm{CDF}_{\NormalDistribution}^{-1}(\beta)$
which requires inversion of the \gls{CDF} of a normal distribution.
However, such an approximation is overly optimistic when $n_{\mathrm{success}}$ approaches the boundaries of its domain (i.e. when $\eta \approx 0$ or $\eta \approx 1$) since normal confidence regions are always symmetrical whereas the actual success rate is inherently bounded as $0 \leq \eta 1$~\citep{Ross2003}.
An alternative method that does not approximate the binomial distribution by a normal one, is the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \code{binofit}).
In particular, this method relies upon the exact binomial distribution, which is why the method is often quoted as the `exact' method.
In particular, the $(1-\alpha)$  confidence bounds on $\eta$ are given by~\citep{Clopper1934}
\begin{align}
 \mathrm{CI}_{\mathrm{ClopperPearson}}  & \isdef \left[ \underline{\eta}, \overline{\eta} \right]\\
 \underline{\eta} &\isdef 
  \mathrm{CDF}_B^{-1}(\alpha/2; n_{\mathrm{success}}, N_{\MC} - n_{\mathrm{success}} + 1)\\
  \overline{\eta} &\isdef
  \mathrm{CDF}_B^{-1}(1-\alpha/2; n_{\mathrm{success}} + 1, N_{\MC} - n_{\mathrm{success}})
\end{align}
where $\mathrm{CDF}_B^{-1}(\alpha; n,m)$ denotes the inverse \gls{CDF} of a $\mathrm{Beta}(n,m)$ distribution that is closely related to the Binomial distribution.
This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\onecolumnwidth]{\thisDir/fig/measurement.pdf}
  \caption[Measurement schematic of \BK\ 1613 filter.]{Schematic representation of the measurement set-up for the \BK\ 1613 filter. The AWG (Arbitrary Waveform Generator) and DAQ (Data Acquisition) hardware share the same clock and are thus synchronized. 
  Blue arrows indicate coax cables. 
  At the output of the bandpass filter, a noise generator is added that buffers the incoming signal using a TL071 opamp and adds white noise before passing the signal to the DAQ.} 
  \label{fig:measurementSetup}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/bode-bk1613.tikz}
  \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.} 
  \TODO{fix figure (maybe downsample logarithmically for efficiency)}
  \label{fig:bk1613}
\end{figure}
